Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
g

In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see appendix XX). Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.

@@

\section{Analysis}
A number of features are excluded before training the model. The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price. A list of the excluded features are found in appendix 11.0.1. The model used for ML are found in appendix 11.0.2.

@@

Firstly, we are somewhat satisfied with the average performance of the model. With an MSE of approximately $55·10^10$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data. 
The curve suggest that we have found the optimal degree of regularization with our hyperparameter. Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit. This is deduced by how poorly the validation predictions performs at smaller lambdas, as opposed to the training performance. On the contrary, had we chosen a greater value of $\lambda$, the model would have been too biased. This is illustrated by how poorly the training data, as well as the validation data, performs at higher values of $\lambda$ . In that case, we would have underfit our model. 
Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting. For the abovementioned reasons, it would not be meaningful to minimize this performance gab by adjusting the hyperparameter. Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to make for more less variance. Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean. As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection. This could be a subject for further studies, to investigate whether this could improve the performance and evaluation of the model. \newline
In conclusion, it would seem that we have found the hyperparameter which yields the optimal bias-variance-trade-off. We can thus conclude that we have optimized our model under the given circumstances.

The learning-curve is depicted in figure \textcolor{red}{XX}

@@

\subsection{Model Selection}
Instead of only assessing the different models by MAE and RMSE.
The Information criteria of the respective models could have been introduced. Which could have altered the selection of preferred model. Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model. As both measurement are increasing in numbers of estimated parameters.

>>>>

In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see appendix XX)}. Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.

@@

\section{Analysis}
A number of features are excluded before training the model. The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the target variable. A list of the excluded features are found in appendix 11.0.1. The model used for ML are found in appendix 11.0.2.

@@

Firstly, we are somewhat satisfied with the average performance of the model. With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data. 
The curve suggest that we have found the optimal degree of regularization with our hyperparameter. Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit. This is deduced by how poorly the validation predictions performs at smaller lambdas, as opposed to the training performance. On the contrary, had we chosen a greater value of $\lambda$, the model would have been too biased. This is illustrated by how poorly the training data, as well as the validation data, performs at higher values of $\lambda$ . In that case, we would have underfit our model. 
Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting. For the abovementioned reasons, it would not be meaningful to minimize this performance gab by adjusting the hyperparameter. Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to make for more less variance. Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean. As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection. This could be a subject for further studies, to investigate whether this could improve the performance and evaluation of the model. \newline
In conclusion, it would seem that we have found the hyperparameter which yields the optimal bias-variance-trade-off. We can thus conclude that we have optimized our model under the given circumstances.

The learning-curve is depicted in figure \textcolor{red}{XX}
\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.6]{Learncurvridge.png}
%\source{}
\end{figure}

@@

\subsection{Model Selection}
Instead of only assessing the different models by MAE and RMSE.
The Information criteria of the respective models could have been introduced. Which could have altered the selection of preferred model. Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model. As both measurement are increasing in numbers of estimated parameters\footnote{Peckov, Aleksandar. (2012)  \textit{A Machine Learning Approach To Polynomial Regression}}.
